\documentclass[12pt]{article}

\usepackage[margin=1in, paperwidth=8.5in, paperheight=11in]{geometry}
\usepackage{amsfonts}
\usepackage{amssymb}
\usepackage{centernot}
\usepackage{amsmath}
\usepackage{pifont}
\usepackage{minted}
\usepackage{xcolor}
\usepackage{mdframed}
\usepackage{graphicx}
\usepackage{fancyhdr}

\pagestyle{fancy}
\chead{CS 202 - ASSIGNMENT 1}

\begin{document}

\noindent
Create a subdirectory of your home directory titled \texttt{aug29}. Inside,
place your solutions to the problems listed below, naming the files
\texttt{p01.c}, \texttt{p02.c}, etc. Your solutions are due on Wednesday,
August 29 before class starts.

\begin{enumerate}
  % Done
  \item (1 point) Write a C program that prints the size, as well as the minimum and
    maximum values of the following data types:
    \begin{itemize}
      \item \texttt{int}
      \item \texttt{unsigned int}
      \item \texttt{unsigned char}
      \item \texttt{double}
      \item \texttt{unsigned short int}
    \end{enumerate}
    Direct your output to \texttt{stdout}. Hint: Read \texttt{man sizeof} and
    investigate the \texttt{limits.h} header.

  % Done
  \item (2 points) Write a C program that reads an integer from \texttt{stdin} and prints
    to \texttt{stdout} if it is even or odd. Hint: investigate the modulus
    operator (\texttt{\%}).

  % Done
  \item (2 points) Write a C program that reads a character from \texttt{stdin} and prints
    to \texttt{stdout} if it is lower case, upper case, a digit, or a special
    character. Hint: read \texttt{man ascii}.

  % Done
  \item (3 points) Write a C program that reads three integers as command line arguments
    and prints to \texttt{stdout} the average, minimum, and maximum of the
    integers.

  % Done
  \item (3 points) Write a C program that reads an integer representing a number of days
    as a command line argument. Convert the integer to weeks and years. Print
    the days, weeks, and years to \texttt{stdout}.
  
  % Done
  \item (3 points) Write a C program that reads three integers \texttt{a}, \texttt{b}, and
    \texttt{c} as command line arguments and
    prints to \texttt{stdout} whether both, one, or neither of \texttt{a} and
    \texttt{b} are exactly divisible by \texttt{c}.

  % Done
  \item (3 points) Write a C program that reads both the cost and selling price of an item
    as command line arguments. Print to \texttt{stdout} either profit or loss.

  % Done
  \item (3 points) Write a C program that accepts three command line arguments
    representing the angles of each corner of a triangle. Print to
    \texttt{stdout} if it is equilateral, isosceles or scalene triangle. Hint:
    floating point numbers should be used.

\end{enumerate}

\end{document}
