\documentclass[12pt]{article}

\usepackage[margin=1in, paperwidth=8.5in, paperheight=11in]{geometry}
\usepackage{amsfonts}
\usepackage{amssymb}
\usepackage{centernot}
\usepackage{amsmath}
\usepackage{pifont}
\usepackage{xcolor}
\usepackage{mdframed}
\usepackage{graphicx}
\usepackage{fancyhdr}

\pagestyle{fancy}
\chead{CS 202 - Assignment 2 (20 points)}

\begin{document}

\noindent
Create a subdirectory of your home directory called \texttt{a2} and place
within it your solutions to the problems below. Name your programs
\texttt{p01.c}, \texttt{p02.c}, etc. Be sure to check for command line
argument, input, and file opening errors, and display helpful error messages.
As always, pay close attention to indentation and spacing within your programs.

\begin{enumerate}
  % Question 1
  \item (1 point) Write a C program that prints all command line arguments, one per line.
    Note that the first command line argument is
    \texttt{argv[1]}. Hint: use \texttt{\%s} as format specifier in
    \texttt{printf}.
  % Question 2
  \item (1 point) Write a C program that reads one integer $n$ as a command line
    argument and prints ``Hello, World!'' $n$ times. Example output: \\ \\
    \texttt{> ./p02 5 \\ Hello, World! \\ Hello, World! \\ Hello, World! \\ Hello, World! \\ Hello, World!}
  % Question 3
  \item (1 point) Write a C program that reads two integers, $n$ and $m$, as command line
    arguments and prints integers $1 \dots n$ in steps of $m$, one per line.
  % Question 4
  \item (1 point) Write a C program that reads one integer $n$ as a command line argument
    and prints $n$, $n^2$, $n^3$, $n^4$, one per line.
  % Question 5
  \item (2 points) Write a C program that reads one integer $n$ as a command
    line argument and prints out all prime numbers below $n$, one per line.
  % Question 6
  \item (2 points) Write a C program that opens and reads a file, named as a
    command line argument, one character at a time and counts the number of
    non-alphabetical characters. Print the count.
  % Question 7
  \item (2 points) Write a C program that opens and reads a file, named as a
    command line argument, one character at a time and prints all uppercase
    characters found.
  % Question 8
  \item (2 points) Write a C program that opens and reads a file named as a
    command line argument. Count the number of occurrences of the following
    words:
    \begin{itemize}
      \item is
      \item and
      \item or
    \end{itemize}
    Print the count.
  % Question 9
  \item (2 points) Write a C program that opens and reads a file named as a command line
    argument and count the number of words in the file. Print the count.
  % Question 10
  \item (2 points) Write a C program that reads one integer at a time from
    \texttt{stdin} and prints the maximum and minimum integers read.
  % Question 11
  \item (2 points) Write a C program that reads an integer $n$ as a command
    line argument. Print an $n \times n$ matrix of \texttt{*}'s.
  % Question 12
  \item (2 points) Write a C program that reads two integers $n$ and $m$ as command
    line arguments. Print an $n \times m$ matrix of \texttt{*}'s.
\end{enumerate}

\end{document}
